%
% Evan Borgstrom's CV
% http://borgstrom.ca/
% evan@borgstrom.ca
%
% Copyright 2015 Evan Borgstrom
%

\documentclass{eab-cv}

\name{Evan Borgstrom}
\location{San Francisco, CA}
\email{evan@borgstrom.ca}

\statement{
    I'm a passionate technologist who fully embraces open-source and its ideologies.  A hacker who is constantly
    striving for excellence.  An engineer who is obsessed with automating any repeatable task.

    I'm fascinated by how complex computer systems operate, and equally as fascinated with how businesses operate.  I'm
    as comfortable talking to executives as I am talking to engineers.
}

\begin{document}

\maketitle

\addheadertext{Recent History}

\timelineitem{2016}{
    \addsubheader{NerdWallet}
    Joined NerdWallet in the capacity of Principal Engineer to build a highly scalable software delivery pipeline, based
    on immutable and ephemeral run time (a la containers), with infrastructure defined via code, and presented as a
    cohesive platform to our Engineering teams.
}

\timelineitem{2014}{
    \addsubheader{LinkedIn}
    Relocated to San Francisco to join LinkedIn in their Site Reliability Engineering group.  Focused on automation at
    the scale of tens of thousands, and driving change to build more efficient systems for running a large, massively
    distributed set of service oriented applications.
}

\timelineitem{2012}{
    \addsubheader{Art + Technology}
    My interest in hardware hacking led me to collaborate with some amazing artists on a number of art projects that
    were built upon a technology foundation.

    The \href{http://knitterstream.borgstrom.ca/}{Knitter Stream} is a hacked knitting machine that knits tweets from
    Twitter.  It was built for the C2MTL conference. \href{https://github.com/borgstrom/KnitterStream}{Full source is
    available on GitHub}. (Arduino + Python)

    The Mood Mixer was a project built using OSC and Max MSP with Ableton Live to create user generated sound and
    visuals.  It lived at the 2012 Luminato Festival in Toronto. (Max MSP + Python).
}

\timelineitem{2009}{
    \addsubheader{Focusing on automation}
    Led the design and development of systems to automate the provisioning, management and trouble response within a
    virtualized environment (Xen, then KVM) for the purpose of hosting web sites \& applications.  Created a custom
    "private cloud" on top of leading open source automation tools.
}

\timelineitem{2007}{
    \addsubheader{FatBox Founded}
    Founded and built a Managed Services company focused on providing technology solutions to the creative services
    industry.

    Built relationships with some of Toronto's most awarded creative agencies, providing all infrastructure required for
    digital projects.
}

\timelineitem{2000}{
    \addsubheader{UUNet / MCI / Verizon Business}
    Held a variety of roles ranging from CTAC to Sr. UNIX Admin to System Architect.  Consistently met and exceeded KPI
    for growth in all roles and was frequently recognized by peers through company programs.
}

\timelineitem{1990's}{
    \addsubheader{Mac SE, Tandy, Commodore 64, DOS, Basic, FreeBSD, Linux, Networking, Perl}
    An obsession begins...
}

\stoptimeline

\addheadertext{Skill Highlights}

\addsubheader{Open Source}
Avidly contributing to Open Source since 2002.  Original author of the
\href{http://borgstrom.ca/qregex.patch-20020129.txt}{Qmail Qregex patch}.  Author of numerous Python \& Django packages
available on PyPI.  Evangelist and contributor to \href{http://saltstack.org/}{SaltStack}
\href{https://github.com/saltstack/salt/commit/744fc0bd32d6f527c1f9e12cdca5bc7ab68f351e}{since 2012}.

\addsubheader{Programming}
Avid programmer interested in all languages \& platforms.  Currently loving Python and very interested in Go.  Previous
experience with Javascript, Perl, Bash, Ruby, C and PHP.

\addsubheader{Markup}
Proficient in many structured markup languages: HTML, XML (yuck), CSS, Sassy CSS, YAML, JSON, Restructured Text,
Markdown, \LaTeX.

\addsubheader{Operating Systems}
Linux administrator since 1998.  Expert Debian \& CentOS skills.  Have run Solaris since version 6.  Previously ran both
FreeBSD, OpenBSD \& Gentoo in production.  Expert understanding of very low level operating system concepts with the
ability to troubleshoot and debug any issue that may arise.

\addsubheader{Networking}
Experience managing both corporate, access \& transit networks.  Comfortable administrating Cisco, Juniper \& Force10
devices.  Working knowledge of many of protocols.  Comfortable both reading \& interpreting as well as authoring \&
contributing to RFC documents.

\addsubheader{Personality}
Calm and collected, able to operate under high pressure situations as well as within tight project constraints.  I
highly value intelligence and love having my opinion altered by a logical presentation of an alternate opinion.

\addsubheader{Language} Strong written \& verbal English skills.  Basic verbal French skills.

\end{document}

% vim: set ft=tex ts=4 sw=4 sws=4 et spell :
